---
title: "Hello R"
author: "Fatima Tanvir"
date: "Data 2401"
output: 
  html_document: 
    fig_height: 10
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 0 columns. It has 3 varaibles.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Let's plot the data in the star dataset:

```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Let's plot the data in the circle dataset:

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

And next calculate the correlation between `x` and `y` in this dataset
 
```{r cor-circle}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Lastly, let's plot the data for all our datasets:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

And next calculate the correlation between `x` and `y` for all datasets!
 
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```